\documentclass[margin,line]{res}
\usepackage{times}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=5.2in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jinwoong Kim\vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}
\vspace{.05in}

\begin{tabular}{@{}p{3.5in}p{3in}}
Naver Green Factory, 6, Buljeong-ro, Bundang-gu & {\it http://} github.com/jinwoongkim \\
Seongnam-si, Gyeonggi-do, 13561, South Korea & {\it E-mail:}  aragnom@gmail.com \\
\end{tabular}

\section{\sc Experience}
{\bf Machine Learning Research Engineer at Naver Corp.} \hfill {\it Sep 2017 - Present} \\
Full time (Ai Suite team, System&Solution) \\
- Developed a monitoring system that monitors the multi-tenant GPU cluster and machine learning workloads using Nvidia DCGM (Data Center GPU Managers) \\
- To maximize the GPU utilization, developed a GPU sharing services using Nvidia MPS so that multi-tenants can run their jobs together on the same GPU\\
- Developed a Kubernetes-based multi-tenant GPU clusters\\

{\bf Machine Learning Research Engineer at Naver Corp.} \hfill {\it Sep 2017 - June 2019} \\
Full Time, (NSML team, Clova AI)  \\
- Developed AutoML framework that tunes hyper-parameter automatically on the multi-tenant GPU cluster \\
-- Published a paper and demonstrated at Sysml2019 \\
-- Presented at Deview 2018 \\
- Developed scheduler and monitoring systems for NSML which is a machine learning framework for a multi-tenant GPU cluster \\
-- Published papers \\
- Setup visualization panels using ELK \\

%\section{\sc Objective}
%Seeking a position in the emerging field of high performance systems
%Seeking a project lead position in the emerging field of
%high performance systems

\section{\sc Education}

{\bf Ms-Ph.D Program in Computer Science and Engineering} \hfill {\it Mar 2011 - Aug 2017 } \\
{\em Ulsan National Institute of Science and Technology (UNIST)}\\
{\em Thesis Title : "Exploiting Graphics Processing Units for Massively Parallel \\ Multi-Dimensional Indexing"} \\
\vspace{.2in}
{\em Advisor : Prof. Beomseok Nam} \\
{\bf B.S. in Computer Engineering} \hfill {\it Mar 2005 - Feb 2011 } \\
{\em Chungbuk National University, South Korea}
\vspace{.05in}

\section{\sc Research Interests}
Database Systems\\
Distributed and Parallel Systems \\
Parallel Multi-dimensional Indexing on the GPU\\
%Distributed Semantic Caching Frameworks\\
Non-Volatile Memory based Logging\\
%Distributed Graph Processing Systems\\
Automatic Machine Learning\\
Large Scale Cluster Scheduler\\
Machine Learning Platform\\

\section{\sc Journal Reviewing Activites}

\begin{enumerate}

\item ACM Transactions on Storage (TOS), 2019
\item IEEE Transactions on Knowledge and Data Engineering (TKDE), 2018

\end{enumerate}

\section{\sc Academic/\\Research Experience}

{\bf Research Intern}  \\
{Carnegie Mellon University, Pittsburgh, PA, USA(Prof. Andrew Pavlo)} \hfill {\it May - Aug, 2015}\\
Designed and developed the in-memory database system, {\it Peloton}
\begin{list2}
\item Implemented the Catalog, DDL, DML, Bootstrap, Logging, etc.
\item Designed the non-volatile memory based logging, {\it Write-Behind Logging}, VLDB, 2016.
\end{list2}

{\bf Visiting Research Scholar}  \\
{University of California Berkeley, Berkeley, CA, USA(Prof. Ikhlaq Sidhu)} \hfill {\it Nov 2015 - Jan 2016}\\

{\bf Research Assistant}  \\
{\it Data Intensive Computing Lab, UNIST} \hfill  {\it Spring 2011 - Fall 2017}\\
\begin{list2}
\item Designed and implemented parallel indexing schemes for multi-dimensional range query processing on the GPU 
\item Implemented a distributed semantic caching framework for MapReduce
\item Worked on multi-dimensional query processing with distributed cache infrastructure in cloud environments
\item Implemented non-volatile memory based {\it Heap manager} to improve logging performance for SQLite
\end{list2}

{\it Korea Institute of Science and Technology Information (KISTI) } \hfill  {\it May 2015 - Nov 2015}\\
\begin{list2}
\item Designed and implemented the GPU-based multi-dimensional indexing for {\it GLOVE}
\end{list2}

{\it LG Electronics (CTO)} \hfill  {\it Jan 2015 - Jun 2015}\\
\begin{list2}
\item Worked on multi-thread query processing for SQLite.
\end{list2}

{\bf Teaching Assistant} \\
%\hspace*{\fill}
\vspace{-.1in}
\begin{list2}
\item {TA for Prof. Beomseok Nam, Object-Oriented Programming } \hfill {\it Spring 2014}
\item {TA for Prof. Beomseok Nam, Advanced Programming } \hfill {\it Fall 2013}
\item {TA for Prof. Beomseok Nam, Introduction to Database Systems } \hfill{\it Winter 2012}
\item {TA for Prof. Tsz-Chiu Au, Engineering Programming } \hfill {\it Fall 2012}
\item {TA for Prof. Young-ri Choi, Engineering Programming } \hfill {\it Spring 2012}
\item {TA for Prof. Beomseok Nam, Engineering Programming } \hfill {\it Fall 2011}
\end{list2}

\section{\sc Honors and Awards}

{\bf Naver WoW Project 2nd Prize, Naver Corp.\hfill {\it 2019} \\
{\bf Naver PhD Fellowship}, Naver Corp.\hfill {\it 2016} \\
{\bf Prof. Ram Kumar Fellowships at ICDE}, Ramkumar Foundation.\hfill {\it 2015} \\
{\bf Merit-based Scholarship}, Chungbuk National University \hfill {\it Spring 2009} \\
{\bf Merit-based Scholarship}, Chungbuk National University \hfill {\it Fall 2008} 

\section{\sc Publications and Preprints}

\begin{enumerate}

\item[16] Heungseok Park, {\bf Jinwoong Kim}, Minkyu Kim, Ji-Hoon Kim, Jaegul Choo,
Jung-Woo Ha, and Nako Sung ``VisualHyperTuner: Visual Analytics for User-Driven
Hyperparameter Tuning of Deep Neural Networks'', 2nd SysML Conference {\bf
(SysML)}, Demo, Stanford, CA, USA, Apr. 2019.

\item[15] {\bf Jinwoong Kim}, Minkyu Kim, Heungseok Park, Ernar Kusdavletov,
Dongjun Lee, Adrian Kim, Ji-Hoon Kim, Jung-Woo Ha, and Nako Sung ``CHOPT :
Automated Hyperparameter Optimization Framework for Cloud-Based Machine
Learning Platforms'', arXiv:1810.03527, 2018

\item[14] Hanjoo Kim, Minkyu Kim, Dongjoo Seo, {\bf Jinwoong Kim}, Heungseok Park, Soeun
Park, Hyunwoo Jo, KyungHyun Kim, Youngil Yang, Youngkwan Kim, Nako Sung, and
Jung-Woo Ha ``NSML: Meet the MLaaS platform with a real-world case study'',
arXiv:1810.09957, 2018

\item[13] {\bf Jinwoong Kim} and Beomseok Nam,
``Co-Processing Heterogeneous Parallel Index for Multi-Dimensional Datasets'',
Journal of Parallel and Distributed Computing{\bf(JPDC)}, Vol. 113, pp 195-203,
Mar. 2018.

\item[12] Nako Sung, Minkyu Kim, HyunWoo Jo, Youngil Yang, {\bf Jinwoong Kim},
Leonard Lausen, Youngkwan Kim, Gayoung Lee, Donghyun Kwak, Jung-Woo Ha, and
Sung Kim, ``NSML: A Machine Learning Platform That Enables You to Focus on Your
Models'', ML System Workshop at NIPS, 2017

\item[11] Wook-Hee Kim, Jihye Seo, {\bf Jinwoong Kim}, and Beomseok Nam,
``clfB-tree: Cacheline Friendly Persistent B-tree for NVRAM'', To appear in ACM
Transactions on Storage{\bf (TOS)}, Special issue on NVM and Storage, 2017.

\item[10] Moohyeon Nam, {\bf Jinwoong Kim}, Beomseok Nam ``Parallel Tree
Traversal for Nearest Neighbor Query on the GPU'' 45th International Conference
on Parallel Processing {\bf (ICPP)}, Philadelphia, PA, USA, Aug. 2016.

\item[9] Wookhee Kim, {\bf Jinwoong Kim}, Woongki Baek, Beomseok Nam and Youjip
Won ``NVWAL: Exploiting NVRAM in Write-Ahead-Logging '' 21st International
Conference on Architectural Support for Programming Languages and Operating
Systems {\bf(ASPLOS)}, Atlanta, GA, USA, Apr. 2016

\item[8] {\bf Jinwoong Kim}, Sehoon Lee, Joong-Youn Lee, Beomseok Nam, Min Ah
Kim ``GLOVE: An Interactive Visualization Service Framework with
Multi-Dimensional Indexing on the GPU '' 27th International Conference for High
Performance Computing, Networking, Storage and Analysis{\bf (SC)}, Poster,
Austin, TX, Nov. 2015.

\item[7] {\bf Jinwoong Kim}, Won-Ki Jeong, and Beomseok Nam ``Exploiting
Massive Parallelism for Indexing Scientific Datasets on the GPU'' IEEE
Transactions on Parallel and Distributed Systems{\bf (TPDS)}, Vol. 26, No. 8,
pp 2258-2271, Aug. 2015. {\bf (Selected as the featured paper of Aug. 2015
issue)}

\item[6] Youngmoon Eom, {\bf Jinwoong Kim}, and Beomseok Nam
``Multi-dimensional Multiple Query Scheduling with Distributed Semantic Caching
Framework'' Cluster Computing, Vol. 18, No. 3, pp 1141-1156, Springer, Jun. 2015.

\item[5] Youngmoon Eom, {\bf Jinwoong Kim}, Deukyeon Hwang, Jaewon Kwak, Minho
Shin, Beomseok Nam ``Improving Multi-dimensional Query Processing with Data
Migration in Distributed Cache Infrastructure'', 21st IEEE International
Conference on High Performance Computing (HiPC 2014)(23\% a/r). Goa, India, Dec. 2014.

\item[4] Youngmoon Eom, Jonghwan Moon, {\bf Jinwoong Kim}, Beomseok Nam,
``Collaborative Multi-dimensional Dataset Processing with Distributed Cache
Infrastructure in the Cloud'', 2nd International Workshop on Autonomic
Management of Grid and Cloud Computing (AMGCC'14) (in conjunction with IEEE CAC
2014), London, UK, Sep. 2014.

\item[3] {\bf Jinwoong Kim}, Sul-Gi Kim, Beomseok Nam, ``Parallel
Multi-dimensional Range Query Processing with R-Trees on GPU'', Journal of
Parallel and Distributed Computing {\bf (JPDC)}, Vol. 73, Issue 8, 1195-1207,
Elsevier, Aug, 2013.

\item[2] Beomseok Nam, Deukyeon Hwang, { \bf Jinwoong Kim}, and Minho Shin,
``High-Throughput Distributed Query Scheduling with EMA-based Statistical
Prediction'', Special Issue on Data Intensive eScience, Distributed and
Parallel Databases, Vol. 30, issue 5--6, pp 401-414, Springer, Jun. 2012.

\item[1] {\bf Jinwoong Kim}, Sumin Hong, and Beomseok Nam ``A Performance
Study of Traversing Spatial Indexing Structures in Parallel on GPU'', 3rd
International Workshop on Frontier of GPU Computing (FGC), in conjunction with
HPCC 2012, Liverpool, UK, Jun. 2012.

\end{enumerate}

\section{\sc Invited Talks}

\begin{enumerate}

\item[4]  Naver AI Techtalk, UNIST, South Korea, Dec. 2019.

\item[3]  "NSML: Machine learning as a platform \& Automize Model Tuning" DEVIEW, South Korea, Oct. 2018.

\item[2]  "NSML: A Machine Learning Platform That Enables You to Focus on Your
Models" The 9th Asian Conference on Machine Learning {\bf (ACML)}, Poster, South Korea, Nov. 2017.

\item[1] "Exploiting Massive Parallelism for Indexing Multi-dimensional
Datasets on the GPU" Parallel Data Lab {\bf (PDL)} at CMU, Pittsburgh, PA, USA, Aug.
2015.

\end{enumerate}


\section{\sc Skills}
\begin{list2}
\item Programming Languages : \\
   C/C++/C\#, Python, CUDA, Go\\
\item Libraries, and Knowledge: \\
   SQL, MPI, Docker, Nvidia MPS, DCGM \\
	Linux, Git, LaTex, ELK, Yarn, Kubernetes \\
\end{list2}

\section{\sc References}

\begin{list2}
\item {\bf Beomseok Nam}\\
Associate professor \\
College of Software \\
Sungkyunkwan University, Suwon, South Korea \\
E-mail: bnam@skku.edu\\

%Department of Computer Science and Engineering \\
%School of Electrical and Computer Engineering\\
%Ulsan National Institute of Science and Technology(UNIST), Ulsan, South Korea \\
%E-mail: bsnam@unist.ac.kr\\

\item {\bf Won-Ki Jeong}\\
Associate professor \\
Department of Computer Science and Engineering \\
Korea University, Seoul, South Korea \\
E-mail: wkjeong@korea.ac.kr \\

\item {\bf Woongki Baek}\\
Associate Professor\\
Department of Computer Science and Engineering \\
School of Electrical and Computer Engineering\\
Ulsan National Institute of Science and Technology (UNIST), Ulsan, South Korea \\
E-mail: wbaek@unist.ac.kr \\

\item {\bf Andrew Pavlo}\\
Assistant Professor\\
Department of Computer Science\\
Carnegie Mellon University, Pittsburgh, USA\\
E-mail: pavlo@cs.cmu.edu\\
\end{list2}


\noindent
{\em Last updated on} {\bf \today}

\vspace*{.5in}

\noindent

\end{resume}
\end{document}


